### 2021-01-12 ch04_papers_ecs_tcr_assessment/papers_ecs_tcr_assessment.tex
Added ECS and TCR table
Added correct ECS and TCR tables for CMIP5 and 6

>>>>

\begin{table}[t]
  \centering
  \csvreader[ECSAndTCRTable]{
    ch04_papers_ecs_tcr_assessment/data/CMIP5_ecs-tcr.csv}{}{
    \dataset & \idx & \ecs & \tcr}
  \caption{\acf{ECS} and \acf{TCR} evaluated for the \acs{CMIP}5 models.
    Details on the calculation on \acs{ECS} and \acs{TCR} are given in
    \cref{subsec:02:ecs} and \cref{subsec:02:tcr}, respectively.}
  \label{tab:04:ecs_tcr_cmip5}
\end{table}

\begin{table}[t]
  \centering
  \csvreader[ECSAndTCRTable]{
    ch04_papers_ecs_tcr_assessment/data/CMIP6_ecs-tcr.csv}{}{
    \dataset & \idx & \ecs & \tcr}
  \caption{As in \cref{tab:04:ecs_tcr_cmip5} but for the \acs{CMIP}6 models.}
  \label{tab:04:ecs_tcr_cmip6}
\end{table}
